### 2013-02-12 exam5/1.tex
start on new exam

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\ifrubric
\centerline{\Large CSU2510H Exam 1 Rubric -- Spring 2012}

\else
\centerline{\Large CSU2510H Exam 1 -- Spring 2012}

@@

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 18\\ \hline
2 & & 10\\ \hline
3 & & 15\\ \hline
4 & & 15\\ \hline
5 & & 18\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 76+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\fi

% \noindent
% {\bf Home on the Range}

% Come up with funny story here.

% \newpage
\begin{problem}\pts{18} % same as on the previous exam :)

Here is a data definition for a class of objects.  It intentionally
uses meaningless names to test whether you've sufficiently
internalized the data-driven development process we've talked about
since the Fall.

\begin{verbatim}
;; A P is one of:          
;; - A                  ;; An A is a (new a% String)
;; - B                  ;; A  B is a (new b% String A)
;; - C                  ;; A  C is a (new c% P)

(define-class a% (fields w))
(define-class b% (fields x y))
(define-class c% (fields z))
\end{verbatim}

\noindent
Design the following methods for \verb|P|s:

\begin{enumerate}

\item \verb|size| - the size of an \verb|A| is $5$; the size of a
  \verb|B| is $8$, regardless of what's inside; and the size of a
  \verb|C| contributes $1$ to the size of the \verb|P| inside.

\item \verb|replace-x| - produces a \verb|P| like this one, but
  with any \verb|x| field replaced by the given string.

\item \verb|same-x-and-w?| - given two strings, produce true if this
  \verb|P| contains a \verb|B| whose \verb|x| is equal to the
  first given string and whose \verb|y| is an \verb|A| whose
  \verb|w| is equal to the second given string.  Produces false
  otherwise.

Be sure to define any interfaces you need and say which classes
implement which interfaces so that your program treats all values
according to their interface.

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
[Here is some more space for the previous problem.]
\newpage
\fi

\begin{solution}
\begin{verbatim}
;;> [6 pts -- contract and purpose for each method]
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-x : String -> P
;;   Replace x field (if any) of this P with given string.
;; - same-x-and-w? : String String -> Boolean
;;   Is there a B within this P with given x field and w field?

;;> [0 pts -- not required, but write something]
;; An A implements:
;; - w : -> String
;;   Get the w string.

;;> [2 pts] In a%: 
(define (size) 5)
(define (replace-x str) this)
(define (same-x-and-w? g c) false)

;;> [3 pts] In b%:
(define (size) 8)
(define (replace-x str)
  (new b% str (this . y)))
(define (same-x-and-w? g c)
  (and (string=? g (this . x))
       (string=? c (this . y . w))))

;;> [4 pts] In c%:
(define (size) (add1 (this . z . size)))
(define (replace-x str)
  (new c% (this . z . replace-x str)))
(define (same-x-and-w? g c)
  (this . z . same-x-and-w? g c))

;; tests
;;> [3 pts -- 1 per method]

\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem}\pts{10}

Here are data, class, and interface definitions for a list of numbers:
\begin{alltt}
;; An LoN is one of:
;; - (new mt%)
;; - (new cons% Number LoN)
;; and implements:
;; - sum : -> Number
;;   Compute the sum of the numbers in this list.
;; - sqrs : -> LoN
;;   List of squares of each number in this list.

(define-class mt%
  (define (sum) 0)
  (define (sqrs) this))

(define-class cons%
  (fields first rest)
  (define (sum)
    (+ (this . first)
       (this . rest . sum)))
  (define (sqrs)
    (new cons% 
         (sqr (this . first)) ; (sqr x) = x\(\sp{2}\)
         (this . rest . sqrs))))
\end{alltt}
%
Here are some examples:
\begin{verbatim}
(check-expect ((new mt%) . sum) 0)
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sum)  9)
(check-expect ((new mt%) . sqrs) (new mt%))
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sqrs)
              (new cons% 16 (new cons% 25 (new mt%))))
\end{verbatim}

\newpage
\noindent
Develop the \verb|sum-sqrs| method that computes the sum of the
squares of a list of numbers.  Here is an example:
\begin{verbatim}
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sum-sqrs) 
              (+ 16 25))
\end{verbatim}

If you can, define a super class of \verb|mt%| and \verb|cons%| and
lift the definition of \verb|sum-sqrs| to this class.  (We will assume
the appropriate \verb|super| declaration in \verb|mt%| and
\verb|cons%|.)  If you cannot, define methods in both \verb|mt%| and
\verb|cons%| for partial credit.

\begin{solution}
\begin{verbatim}

;; [2 pts% -- class def]
(define-class list%
  ;; [2 pts -- contract and purpose]
  ;; sum-sqrs : -> Number
  ;; compute the sum of the squares of the numbers in this list
  ;; [4 pts -- implementation]
  (define (sum-sqrs)
    ((this . sqrs) . sum)))

;; [2 pts -- tests]
(check-expect ((new mt%) . sum-sqrs) 0)
\end{verbatim}
\end{solution}

\newpage

\end{problem}

@@

In order to manage class scheduling, the College decided that they
needed to create a new implementation of the \verb|Set| data
structure.  They went with the lowest bidder, which
turned out to be a bunch of BU students.  Now, having paid for this
code, the College needs to test it, and they turn to you.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{problem} \pts{18}
Last night, Asumu was up late improving the {\tt class} languages.
Unfortunately, he was too tired to test his work, and his last commit
broke the numeric system.
%
This puts us in the dire position of no longer being able to calculate
the factorial of large numbers, and we turn to you for help.

This is the definition of a class of functional objects
with a {\tt fact} method:

\begin{verbatim}
;; A Fact is (new fact%) and implements 
;; - fact : Natural -> Natural
;;   Compute n!.
(define-class fact%
  (define (fact n)
    (cond [(zero? n) 1]
          [else (* n (this . fact (sub1 n)))])))

(check-expect ((new fact%) . fact 0) 1)
(check-expect ((new fact%) . fact 5) 120)
\end{verbatim}

Since we can no longer rely on built in numbers to represent
\verb|Natural|s, we will represent \verb|Natural|s with objects and
then rewrite the \verb|fact| method to operate over this new kind of
data.

Here is the \verb|Natural| interface:

\begin{verbatim}
;; A Natural implements:
;; - zero? : -> Boolean
;;   is this Natural the zero value?
;; - sub1 : -> Natural
;;   produce a natural one less than this natural 
;;   (or zero if this natural is zero)
;; - times : Natural -> Natural
;;   multiply this natural by the given natural
\end{verbatim}

\newpage
Write a new definition of the \verb|fact| method using the
\verb|Natural| interface definition given above, and \emph{not} using
the built-in numbers of the class system or DrRacket.  You can assume
there is a defined constant \verb|one|, which is a \verb|Natural|
object representing $1$.

\begin{verbatim}
(check-expect ((new fact%) . fact one) one)
(check-expect ((new fact%) . fact (one . sub1)) one)
\end{verbatim}

\newpage

Now, design data and class defintions that implement \verb|Natural|, and
supports the methods \verb|zero?|, \verb|sub1|, and \verb|times|.
Define the constant \verb|one|.  (\emph{Hint}: remember that the
natural numbers can be seen as a recursive union; a natural number is
either zero, or one more than a natural number.)

It will be helpful to define the helper methods \verb|add1| and
\verb|plus|.  Also, remember that $n + m = (n-1) + m + 1$ and that $n
\cdot m = (n-1) \cdot m + m$.  Don't overlook the slightly weird
specification for \verb|sub1|: $0-1 = 0$; this weirdness is common
amongst mathematicians when working with natural numbers.

\ifrubric
\else
\newpage
[Here is some more space for the previous problem.]
\newpage
\fi
\end{problem}

\begin{solution}
\begin{verbatim}
;; Part 1: [2 pts]
(define-class fact%
  (define (fact n)
    (cond [(n . zero?) one]
          [else (n . times (this . fact (n . sub1)))])))

;; Part 2:
;; [2 pts -- data defintion]
;; A Natural is one of
;; - (new zero%)
;; - (new succ% Natural)
(define-class zero%
  ;; [4 pts -- methods in zero%]
  (define (sub1) this)
  (define (plus n) n)
  (define (add1) (new succ% this))
  (define (times n) this)
  (define (zero?) true))

(define-class succ%
  (fields pred)
  ;; [7 pts -- methods in succ%]
  (define (zero?) false)
  (define (add1) (new succ% this))
  (define (plus n) (this . pred . plus n . add1))
  (define (times n) (this . pred . times n . plus n))
  (define (sub1) (this . pred)))

(define zero (new zero%))
;; [1 pt -- define one]
(define one (new succ% (new zero%)))

;; [3 pts -- tests]
(check-expect (one . zero?) false)
(check-expect (one . sub1) zero)
(check-expect ((new succ% one) . sub1) one)
(check-expect (zero . zero?) true)
(check-expect (zero . sub1) zero)
\end{verbatim}
\newpage
\end{solution}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 1 \ifrubric (SOLUTION) \fi-- Spring 2013}

@@

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 18\\ \hline
2 & & 10\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 28+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

@@

% Set/Property problem

In order to manage the distribution of ID , the College decided that they
needed to create a new implementation of the \verb|Set| data
structure.  They went with the lowest bidder, which
turned out to be a bunch of BU students.  Now, having paid for this
code, the College needs to test it, and they turn to you.

@@

% JSON problem

@@

@@

% Visitor on Binary Trees
